Walling up Backdoors in Intrusion Detection Systems

### 2019-10-15 paper/paper.tex
Reviewer corrections

As shown in \autoref{fig:pdp_ttl}, the \glspl{pdp} for the \gls{mlp} show a deep notch for certain low values of stdev(TTL). As discussed above, normal traffic is very unlikely to have deviating \gls{ttl} values for different packets. In contrast to \autoref{fig:pdp_ttl}, one would therefore expect this feature to have a negligible influence on the classification result. In our case, this notch thus points to the existence of the backdoor we embedded. For the \gls{rf} model the same pattern is observed but omitted for brevity.

>>>>

As shown in \autoref{fig:pdp_ttl}, the \glspl{pdp} for the \gls{mlp} show a deep notch for certain low values of stdev(TTL). As discussed above, normal traffic is very unlikely to have deviating \gls{ttl} values for different packets. In contrast to \autoref{fig:pdp_ttl}, one would therefore expect this feature to have a negligible influence on the classification result. Hence, in our case,
existence of a backdoor can be assumed since the \gls{pdp} plummets to very low values for a specific value of stdev(TTL) for no apparent reason.

%this notch thus points to the existence of the backdoor we embedded. For the \gls{rf} model the same pattern is observed but omitted for brevity.
